# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
This is time for reading the csv data, separated by comas
```{r}
data<-read.csv("activity.csv", sep=",")
```
We preprocess the data, takking steps and interval as numbers

```{r}
data$steps<-as.numeric(data$steps)
data$interval<-as.numeric(data$interval)
```
## What is mean total number of steps taken per day?
First, we aggregate the data by date to take the sum of steps

```{r}
aggregatedData<-aggregate(. ~ date, data, sum)[1:2]
```

We make a histogram of the total number of steps taken each day

```{r fig.width=10}
library(ggplot2)
g<-ggplot(aggregatedData, aes(date,steps))
g + geom_bar(stat="identity") +
   labs(title = "Total steps per day") +
   labs(x = "Date", y = "Steps") 
```


and calculate the median and the mean of all the days

```{r}
median(aggregatedData$steps)
mean(aggregatedData$steps)
```


## What is the average daily activity pattern?

We Make a time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

Firt, we take the data aggregated by 5-minute intervals
```{r}
dataIntervalAggregated<-data
dataIntervalAggregated$interval<-factor(dataIntervalAggregated$interval)
aggregatedIntervalData<-aggregate(. ~ interval, dataIntervalAggregated, mean)[1:2]
```

We plot the results
```{r fig.width=10}
library(ggplot2)
g<-ggplot(aggregatedIntervalData, aes(interval,steps))
g + geom_bar(stat="identity") +
   labs(title = "Average number of steps every 5-minutes") +
   labs(x = "5-minute intervals", y = "Average number of steps") 
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r}
aggregatedIntervalData[aggregatedIntervalData$steps==max(aggregatedIntervalData$steps),]
```


## Imputing missing values

Calculate and report the total number of missing values in the dataset

```{r}
nrow(data[is.na(data$steps),])
```


We fill all of the missing values in the dataset with the mean for that 5-minute interval.

```{r}
fillNA<-function(data){
    for (i in 1:nrow(data)){
        if (is.na(data[i,]$steps)){
            data[i,]$steps<-aggregatedIntervalData[aggregatedIntervalData$interval==data[i,]$interval,]$steps
        }
    }
    data
}
data<-fillNA(data)
data
```



## Are there differences in activity patterns between weekdays and weekends?
